paper2_resistance_mechanisms_mixtures

### 2017-02-12 inst/documents/paper2/paper2_resistance_mechanisms_mixtures.Rmd
paper writing

#An accessible model to help understand the evolution of insecticide resistance : insecticide effectiveness predicted to be key to the relative performance of mixtures.

@@

>>>>

#Evolution of insecticide resistance with insecticide mixtures and sequences : an accessible model to promote understanding.

#An accessible model to promote understanding of the evolution of insecticide resistance : insecticide effectiveness predicted to be key to the relative performance of mixtures.

@@

### Declarations
TODO see https://malariajournal.biomedcentral.com/submission-guidelines/preparing-your-manuscript/research-article

##### Ethics approval and consent to participate
Not applicable
##### Consent for publication
Not applicable
##### Availability of data and material

##### Competing interests

##### Funding

##### Authors' contributions
AS conceived the paper, re-factored the model code, performed the analyses and wrote the first and subsequent versions of the paper. IH conceived the modelling approach, developed the first version of the model in collaboration with Bethany Levick, explained concepts to AS and reviewed and commented on all manuscript versions.

##### Acknowledgements
Thankyou to Bethany Levick who developed the first version of the model code.
